---
title: "Data Acquisition"
author: "Andrew.Z.Flores"
date: "4/10/2020"
output: html_document
---

```{r, packages}
#Uncomment to install
#install.packages("wordbankr")    
#install.packages("childesr")
```

```{r, libraries}
library(wordbankr) # required to download mcdi forms
library(childesr)  # required to download CHILDES transcripts
```

# Data Acquisition
## Mac Arthur Bates Communicative Inventories (MCDI)
We will begin by downloading all English (American) "Words & Sentences" inventories from wordbank by using the *wordbankr* package and saving the dataset in its raw form.

```{r}
# Download mcdi
get_mcdi <-
  get_instrument_data("English (American)",
                      "WS",
                      administrations = TRUE,
                      iteminfo = TRUE)

#Save file.
write.csv(get_mcdi, file = "raw_mcdi.csv", row.names = FALSE)
```

## Child Language Data Exchange System (CHILDES)
Next we will download all English (American) transcripts using the *childesr* package. This is a large file and make take 5 minutes or so to download.
```{r}
#Download CHILDES utterances
childes_utterance <- get_utterances(collection = "Eng-NA")

#Save file.
write.csv(childes_utterance, file = "raw_childes.csv", row.names = FALSE)
```

## Sensorimotor norms
A series of metrics that quantify six modality specific attributes of words based on adult norming. These can be downloaded from *https://www.lancaster.ac.uk/psychology/lsnorms/*. We will download the entire dataset for use. Hereafter saved as *sensorimotor_norms.csv*.

>Lancaster Sensorimotor Norms
Multidimensional measures of Perceptual and Action Strength for 40,000 English words.

## Concreteness norms
A collection of concretness ratings for 40 thousand English lemma words collected from Amazon Mechanical Turk. The ratings can be downloaded from *http://crr.ugent.be/archives/1330*. Hereafter saved as *concreteness_norms.csv* .

>Concreteness ratings for 40 thousand English lemmas
We have collected concreteness ratings for 40 thousand English lemma words with Amazon Mechanical Turk. The ratings come from a larger list of 63 thousand words and represent all English words known to 85% of the raters. As such, the list can be used as a reference list for future word recognition in (American) English.

## Valence norms
A collection of affective ratings for 14 thousand English words from Amazon Mechanical Turk.
The ratings can be downloaded from *http://crr.ugent.be/archives/1003*. Hereafter saved as *valence_norms.csv*

>In collaboration with Amy Warriner and Victor Kuperman we have collected affective norms of valence, arousal, and dominance for 13,915 English words (lemmas). They are a complement of our age-of-acquisition ratings and subtitle word frequencies. 

## Iconicity norms 
A collection of iconicity (resemblance between form and meaning) word norms from Amazon Mechanical Turk. The ratings can be obtained from the following publication *Perry, L. K., Perlman, M., & Lupyan, G. (2015). Iconicity in English and Spanish and its relation to lexical category and age of acquisition. PloS one, 10(9).*, where you will find a link to the dataset on page 14 under "Supporting Information" & "S1 Data. Data collected in English Experiments 1–3". Hereafter saved as *iconicity_norms.csv*.


